---
title: "Github Projects"
author: "Jesus Alcocer Tagua"
date: "Updated on: `r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    css: styles.css
    toc: true
    toc_float: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE} 
a = knitr::asis_output("\U2714")

#Sys.setlocale("LC_TIME", "English")
```

# Projects


Main github page linking to all my IT related projects.[^2]

Please feel free to copy, modify, distribute and suggest any further improvements on them.[^1]

#### Data analysis related:

 * [Data (financial) analysis with R](https://reisikei.github.io/Financial_analysis_R/)
 
#### Cloud, Linux, Docker related:
 
 * [Docker](https://reisikei.github.io/docker/)
 * [Linux](https://reisikei.github.io/Linux/)
 * [RPi](https://reisikei.github.io/RPi/)
 
#### Engineering related:

 * Bike/Motorbike dynamic simulator - [Multi body system dynamics in Matlab, Python WIP](https://github.com/reisikei/Bike_dynamic_simulator) - To be used as environment for reinforced learning projects.


# Data Sources

Open-source data sets that can be used:

* [US Census Bureau](https://www.census.gov/data.html)
* [EU](https://data.europa.eu/euodp/en/data)
* [Facebook official API](https://developers.facebook.com/docs/graph-api/overview)
* [Amazon AWS open dataset](https://aws.amazon.com/cn/opendata/public-datasets/)
* [Google Finance](https://google.com/finance)
* [ImageNet](https://www.image-net.org/)



# Recommended lecture

* [The signal and the noise](https://www.goodreads.com/book/show/13588394-the-signal-and-the-noise)
* [Fast AI Book](https://github.com/fastai/fastbook)
* [Mathematics for ML](https://mml-book.github.io/)
* [The elements of statistical learning](https://web.stanford.edu/~hastie/ElemStatLearn/)


[^1]: Web version of the outputs generated by the codes posted on <https://github.com/reisikei/reisikei>
[^2]: Contact me on: <https://linkedin.com/in/jalcocer>



